Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-06 sattose/paper.tex
Moving stuff around

@@

A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.

@@

For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. This way we strive to make the problem of duplication in source code easier to deal with.

@@

>>>>

For this research, we strive to improve upon the current state-of-the-art in clone refactoring \cite{fontana2015duplicated, alwaqfi2017refactoring} by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. This way we strive to make the problem of duplication in source code easier to deal with.

@@

\subsubsection{Current clone refactoring tools}
A tool called DCRA (Duplicated Code Refactoring Advisor) looks into refactoring opportunities for clone pairs \cite{fontana2012duplicated}. This tool chooses to only focus on refactoring clone pairs because they argue that \textit{clone pairs are much easier to manage when considered singularly.} As intermediate steps, the authors measure a corpus of Java systems for some clone-related properties of the systems, like the relation (in terms of inheritance) between code fragments in a clone pair.

@@

@@

\subsubsection{Clone types}
In a 2007 survey by Roy et al \cite{roy2007survey} he defines four types of clones:\\
\textbf{Type 1:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type 2:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type 3:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout, and comments.\\
\textbf{Type 4:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.

A higher type of clone means that it's harder to detect. It also makes the clone harder to refactor, as more transformations would be required. Higher clone types also become more disputable whether they actually indicate a harmful antipattern (as not every clone is harmful \cite{jarzabek2010clones, kapser2008cloning}).
